Machine Learning Tools for Open Cluster Characterization with Gaia DR2 Data

### 2021-01-31 paper/paper.tex

%---------------------------
%título del trabajo y autor
%---------------------------
\title{Machine Learning Tools for Open Cluster Characterization with Gaia DR2 Data}
\author{CD. Álvaro, J. Álvaro, CAG. Guzmán}
\date{24th of January, 2021}

@@

Melotte 25 is located at 66.725 degrees in right ascension and 15.867 degrees in
declination with a radius of 165 arcmin and composed by more than 400,000 stars.

@@

All these clusters have a wide variety of diameters, from 25 to 330 arcmin,
as well as the number of stars that belong to them. NGC 2682 has 3,000 stars while
Melotte 25 is composed by more than 400,000 stars. More information about the
studied clusters is available in Table \ref{tab:clusters_summary}.

>>>>

%---------------------------
%título del trabajo y autor
%---------------------------
\title{Machine Learning Tools for Open Cluster Characterization with Gaia DR2 Data}
\author{CD. Álvaro, CAG. Álvarez, J. Álvaro}
\date{24th of January, 2021}

@@

Melotte 25 is located at 66.725 degrees in right ascension and 15.867
degrees in declination with a radius of 165 arcmin.
This region contains more than 400,000 stars.

@@

All these clusters have a wide variety of diameters, from 25 to 330 arcmin,
as well as the number of stars that belong to them. NGC 2682 has 3,000 stars
while Melotte 25 is located inside a region with more than 400,000 stars.
More information about the studied clusters is available in Table \ref{tab:clusters_summary}.
